Robust receding horizon control for linear systems with state dependent disturbance

### 2015-04-08 draft.tex
Added citation.

Notice that in since the right hand side of~\eqref{eq:PWA:def:disturbance} is considered to be piecewise affine, the active 
affine function needs to be determined in a similar fashion. Elementwise $H(x_k(\alpha),u_k(\alpha))$ reduces to 
\begin{equation}
\Resize{
\begin{split}
	H_i(x_k(\alpha),u_k(\alpha)) &= \max_j\{\left(H^x_{i,j} \Psi^x_k +H^u_{i,j}\Psi^u_k\right)x_N(\alpha) + 
	\left(H^x_{i,j} \psi^x_k +H^u_{i,j}\psi^u_k + h_{i,j}\right) \}\\
	&=\max_j f_j\alpha + g_j
	\end{split}
}
\end{equation}
which we can rewrite as
\begin{equation}\label{eq:definition:as:mpLP}
	H_i(x_k(\alpha),u_k(\alpha)) = \left\{\begin{array}{rcl} \min_{(t,\alpha)}& &t\\
	\text{s.t.}& &f_j\alpha+g_j \leq t\; \forall j.\\
	& &0\leq\alpha\leq1
	\end{array}\right.
\end{equation}
So elementwise the determination of the active affine representation is a multi-parametric linear program
that has to be solved in every active set update. So that $W_x^\prime,\,W_u^\prime$ and $w^\prime_c$ remain the active
solution. This can be done by computing the vertices of $\mathcal H = \{(t,\alpha):0\leq\alpha\leq1\wedge
f_j\alpha+g_j\leq t\;\forall j\}$ and ordering the vertices such that $0=\alpha_1\leq\alpha_2\leq\dots$ the solution
that has to be considered in the line search is given by $\alpha_2$.

>>>>

Notice that in since the right hand side of~\eqref{eq:PWA:def:disturbance} is considered to be piecewise affine, the active 
affine function needs to be determined in a similar fashion. Elementwise $H(x_k(\alpha),u_k(\alpha))$ reduces to 
\begin{equation}
\Resize{
\begin{split}
	H_i(x_k(\alpha),u_k(\alpha)) &= \max_j\{\left(H^x_{i,j} \Psi^x_k +H^u_{i,j}\Psi^u_k\right)x_N(\alpha) + 
	\left(H^x_{i,j} \psi^x_k +H^u_{i,j}\psi^u_k + h_{i,j}\right) \}\\
	&=\max_j f_j\alpha + g_j
	\end{split}
}
\end{equation}
which we can rewrite as
\begin{equation}\label{eq:definition:as:mpLP}
	H_i(x_k(\alpha),u_k(\alpha)) = \left\{\begin{array}{rcl} \min_{(t,\alpha)}& &t\\
	\text{s.t.}& &f_j\alpha+g_j \leq t\; \forall j.\\
	& &0\leq\alpha\leq1
	\end{array}\right.
\end{equation}
So elementwise the determination of the active affine representation is a multi-parametric linear program, see e.g.~\cite{Gal:1995},
that has to be solved in every active set update. So that $W_x^\prime,\,W_u^\prime$ and $w^\prime_c$ remain the active
solution. This can be done by computing the vertices of $\mathcal H = \{(t,\alpha):0\leq\alpha\leq1\wedge
f_j\alpha+g_j\leq t\;\forall j\}$ and ordering the vertices such that $0=\alpha_1\leq\alpha_2\leq\dots$ the solution
that has to be considered in the line search is given by $\alpha_2$.
